Exploring Transfer Learning with Fluorescence Cell Image

### 2019-11-27 paper/paper.tex
fix bug
final paper commit hopefully

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{ {figures/} }

@@

\section{General Information}
This project is focusing on building a transfer learning model on biological fluorescence microscope captured images. We plan to test the performance between different layers in a pre-trained model and address how could an optimize for this specific type of image be compared with learning regular images.

\section{Abstract}
Transfer learning is a popular method for tackling machine learning problems with image classification, 
pre-trained models allow people to leverage it's generalization capabilities without needing large compute resources. In this project, we focused on models to classify images of mixed patterns of proteins,
taken with a microscope. To achieve this goal, we utilized transfer learning and demonstrated the hypothesis that earlier layers in a convolutional network capture simple features,
while later layers capture more complex features. Due to the differences between the training set
of the pre-trained model and our dataset, we show that earlier layers in a pre-trained convolutional network
give better results in our classification task. Our best model realized a 94\% accuracy on the test dataset with limited computational sources, thus provided a feasible way for people with no powerful machines.

\section{Introduction}
There are now many neural network methods and architectures designed for image classification that performs exceptionally well. These models were trained
on millions of images, with powerful GPU acceleration. However, in many cases where an individual or group needs a model for an image classification task, these pre-trained models cannot be applied directly. In this case, the usual solution is to use transfer learning. Using the pre-trained model as a feature extractor, we pass our task-specific data into a pre-trained model and then train a linear classifier using the extracted features of our images.
\\
\\
These pre-trained models are usually trained on the ImageNet dataset\cite{imagenet_cvpr09}. This dataset is a large
collection of images of real-world objects such as animals, like dogs and cats, and other objects like cars.
Thus we would expect these models to be good at extracting features from images that are similar to ImageNet,
aka real-world, everyday objects. If we want to apply these models to images that are very different from the ImageNet dataset, such as the Human Protein dataset, we would expect the model to not be able to extract very good features.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{accuray.png}
    \end{subfigure}

@@

\begin{table}[ht]
\centering

\begin{tabular}{|c|c|c|c|c|}
    \hline\\
     Model 1 & Model 2&Model 3&Model 4 \\
     \hline\\
     Error&0.229&0.565&0.314&0.236\\
     \hline\\
     Accuracy&0.946&0.932&0.927&0.936\\
      \hline
     F1 Score&0.321&0.169&0.312&0.267\\
     \hline
\end{tabular}

{\raggedright Table 1: Results of models on test set. Model 1 represents the pre-trained model with the earliest layer, Model 2 with the second earliest layer and so on. \par}

@@

\section{Discuss}
This paper presents a complementary implementation of image identification deep learning model based on the pre-trained and open-sourced residual network ResNet. We built four different models by modified different layer blocks from the ResNet for each of the models. The precision and recall of four different models are close but the first model has the best result on both parts(Accuracy: 0.946 over 0.935 average; Recall 0.299 over 0.336 average). This result reveals that the earlier hidden layers could capture the variance better than the later hidden layers. This output consists of our expectation as the earlier layers focus on the basic features of images. We believe the importance of the entry layers since some of the protein localization patterns from the images are very small and easy to be overlooked. Another challenge is that the images of protein are captured by an automated fluorescence microscopy system and composed of shapes and colors with minor differences. We believe that the feature of source images determined that the earlier layers and learning process may do a more significant impact on the result compared with the later hidden layers.
\\
\\
Even the general output results of the four models are very similar, we still believe that they are enough to support our conjecture. The main reason for this is the whole learning process is all based on ResNet which is a well developed and mature pre-trained model. It won the champion of ILSVRC in 2015, and we believe the performance of ResNet provides a nice basement of high accuracy and low loss output.\cite{winner} Another possible reason we do not have enough comparing test cases.
Due to the high requirement of both CPU and GPU performance of this project, we could only test the model based on our local hardware instead of a cloud machine. The whole test of the current 4 distinct models would take 8 up to over 20 hours to complete. The time and hardware limit the number of tests we could make for this project. We believe when more models could be tested, the performance trend of different layers from front to end would be more observable.
\\
\\
The hardware problem restricts the final F1 score as well. Our current data has an F1 score that varies rapidly from 0.32 to 0.68 when the ideal score should be stabled above 0.70. We compared our code with a published note\cite{note} and we believe the most possible reason is we epoch each model tests too little. To make the test possible to complete locally, we have 10 epoch with a batch size of 32. An ideal epoch number for a project like this should be around 100. Since we only have a 10\% epoch size and based on former tests and researches\cite{100epo}, an unbalanced F1 would possibly happen.
\\
\\
This project is focusing on building a transfer learning model on biological fluorescence microscope captured images. We tested the performance between four different layers in a pre-trained model ResNet50V2 and find that the earlier layer performs better than the latter layers of this specific type of image. To refine this project, more tests based on different layer classifiers should be implemented, and tests with more epoch should be considered. These works are valuable since they could highly robust the conclusion of this paper and verify how similar DNNs should be designed and focused especially those for biological researches. To achieve this, a reliable testing cloud machine should be very useful. Other techniques like clusters and codebooks are also possible options to lower down the source complexity for local tests. This paper provides a possible strategy and idea to solve image recognition problems of high similarity with easy-overlooked critical features.

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[margin=1.25in]{geometry}
\graphicspath{ {figures/} }

@@

%\section{General Information}
%This project is focusing on building a transfer learning model on biological fluorescence microscope captured images. We plan to test the performance between different layers in a pre-trained model and address how could an optimize for this specific type of image be compared with learning regular images.

\begin{centering}
  \section*{Abstract}
\end{centering}

Transfer learning is a popular method for tackling machine learning problems with image classification, 
pre-trained models allow people to leverage it's generalization capabilities without needing large compute resources. In this project, we focused on models to classify images of mixed patterns of proteins,
taken with a microscope. To achieve this goal, we utilized transfer learning and demonstrated the hypothesis that earlier layers in a convolutional network capture simple features,
while later layers capture more complex features. Due to the differences between the training set
of the pre-trained model and our dataset, we show that earlier layers in a pre-trained convolutional network
give better results in our classification task. Our best model realized a 94\% accuracy on the test dataset with limited computational sources, thus provided a feasible way for people with no powerful machines.
\\
\section{Introduction}
There are now many neural network methods and architectures designed for image classification that performs exceptionally well. These models were trained
on millions of images, with powerful GPU acceleration. However, in many cases where an individual or group needs a model for an image classification task, these pre-trained models cannot be applied directly. In this case, the usual solution is to use transfer learning. Using the pre-trained model as a feature extractor, we pass our task-specific data into a pre-trained model and then train a linear classifier using the extracted features of our images.
\\
\\
These pre-trained models are usually trained on the ImageNet dataset\cite{imagenet_cvpr09}. This dataset is a large
collection of images of real-world objects such as animals, like dogs and cats, and other objects like cars.
Thus we would expect these models to be good at extracting features from images that are similar to ImageNet,
aka real-world, everyday objects. If we want to apply these models to images that are very different from the ImageNet dataset, such as the Human Protein dataset, we would expect the model to not be able to extract very good features.

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{accuracy.png}
    \end{subfigure}

@@

  \begin{table}[h!]
    \centering

    \begin{tabular}{|c|c|c|c|c|}
        \hline
         &Model 1 & Model 2&Model 3&Model 4 \\
         \hline
         Loss & 0.229 & 0.565 & 0.314 & 0.236\\
         \hline
         Accuracy & 0.946 & 0.932 & 0.927 & 0.936\\
          \hline
         F1 Score & 0.321 & 0.169 & 0.312 & 0.267\\
         \hline
    \end{tabular}

    \caption {Results of models on test set. Model 1 represents the pretrained model with the earliest layer, Model 2 with the second earliest layer and so on. }

@@

\section{Discussion}
This paper presents a complementary implementation of image identification deep learning model based on the pre-trained and open-sourced residual network ResNet. We built four different models by modified different layer blocks from the ResNet for each of the models. The precision and recall of four different models are close but the first model has the best result on both parts(Accuracy: 0.946 over 0.935 average; Recall 0.299 over 0.336 average). This result reveals that the earlier hidden layers could capture the variance better than the later hidden layers. This output consists of our expectation as the earlier layers focus on the basic features of images. We believe the importance of the entry layers since some of the protein localization patterns from the images are very small and easy to be overlooked. Another challenge is that the images of protein are captured by an automated fluorescence microscopy system and composed of shapes and colors with minor differences. We believe that the feature of source images determined that the earlier layers and learning process may do a more significant impact on the result compared with the later hidden layers.
\\
\\
Even the general output results of the four models are very similar, we still believe that they are enough to support our conjecture. The main reason for this is the whole learning process is all based on ResNet which is a well developed and mature pre-trained model. It won the champion of ILSVRC in 2015, and we believe the performance of ResNet provides a nice basement of high accuracy and low loss output.\cite{winner} Another possible reason we do not have enough comparing test cases.
Due to the high requirement of both CPU and GPU performance of this project, we could only test the model based on our local hardware instead of a cloud machine. The whole test of the current 4 distinct models would take 8 up to over 20 hours to complete. The time and hardware limit the number of tests we could make for this project. We believe when more models could be tested, the performance trend of different layers from front to end would be more observable.
\\
\\
The hardware problem restricts the final F1 score as well. Our current data has an F1 score that varies rapidly from 0.32 to 0.68 when the ideal score should be stabled above 0.70. We compared our code with a published note\cite{note} and we believe the most possible reason is we epoch each model tests too little. To make the test possible to complete locally, we have 10 epoch with a batch size of 32. An ideal epoch number for a project like this should be around 100. Since we only have a 10\% epoch size and based on former tests and researches\cite{100epo}, an unbalanced F1 would possibly happen.
\\
\\
This project is focusing on building a transfer learning model on biological fluorescence microscope captured images. We tested the performance between four different layers in a pre-trained model ResNet50V2 and find that the earlier layer performs better than the latter layers of this specific type of image. To refine this project, more tests based on different layer classifiers should be implemented, and tests with more epoch should be considered. These works are valuable since they could highly robust the conclusion of this paper and verify how similar DNNs should be designed and focused especially those for biological researches. To achieve this, a reliable testing cloud machine should be very useful. Other techniques like clusters and codebooks are also possible options to lower down the source complexity for local tests. This paper provides a possible strategy and idea to solve image recognition problems of high similarity with easy-overlooked critical features.
